---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# HolidayAPI

<!-- badges: start -->
<!-- badges: end -->

The goal of HolidayAPI package is making worldwide holidays / bank days accessible to the R community. The package is an API wrapper of the [Holiday API](https://holidayapi.com/). You can see details of the API documentation and limitations at [https://holidayapi.com/docs](https://holidayapi.com/docs). Be aware that you need a key of the API, which you can get for free at [https://holidayapi.com/signup](https://holidayapi.com/signup).

## Installation

You can install the released version of HolidayAPI from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("matbmeijer/HolidayAPI")
```
## Example

To work, you will need to save your API key - the package automatically loads the key for every function once you have saved the key:

``` r
library(HolidayAPI)
save_key("____YOUR_API_KEY_HERE____")
```

This is a basic example showing how to obtain holiday data for Spain for 2018:

```{r example}
library(HolidayAPI)
df<-get_holidays(country = "ES", year = 2018)
summary(df)
print(df)
```

